---
title: "Statistical Inference Project 2"
author: "Francisco Martín"
date: "October 8, 2018"
output: html_document
---

## Overview

This is the part 1 of the Statistical Inference final project. It consist on a study of the 
R dataset "ToothGrowth", which presents measurements of 60 Guinea Pigs, each 10 at each Vitamin 
C dose level (0.5, 1 and 2 mg) for each type of delivery method (orange juice or ascorbic acid).

## Analysis

### Summary of the data

First of all data should be loaded. Let's look how is it like:

```{r load_data}
library(datasets)
library(ggplot2)
data(ToothGrowth)
summary(ToothGrowth)
head(ToothGrowth)
``` 

There are 30 observations of every type of supply (OJ orange juice or VC ascorbic acid). as there 
are 3 different doses, we can use boxplot to see every one of them

```{r boxplot_doses}
g <-  ggplot(ToothGrowth, aes(x=dose, y=len)) 
g + geom_boxplot(aes(fill=factor(dose)))+facet_grid(.~supp)+xlab("Dose (mg) of vitamin C")+ylab("Tooth length")+ggtitle("Tooth lenght by dose.")
```

### Hypothesis

Once we have seen how data is distributed, let's do some hypothesis. Hypothesis I think is 
reasonable here is that orange juice has a significant impact on tooth lenght compared to 
ascorbic acid. This will be my zero hipothesis H<sub>0</sub>. The non-zero hypothesis will be 
just the opossite: orange juice has no significant impact compared to ascorbic acid. This will 
be H<sub>a</sub>.

Just looking at the data, it looks pretty clear orange juice has a bigger impact when dose is 
smaller than 2mg. But let's test it using t.test just for be sure of that:

```{r testing}
t.test(len ~ supp, data=ToothGrowth[ToothGrowth$dose < 2,])
t.test(len ~ supp, data=ToothGrowth[ToothGrowth$dose == 2,])
```

## Conclusions

Looking at the result of t.test, difference in mean when dose is 2mg is approximately zero, while 
this difference when dose is lower than 2mg is 5.59. Also, 95% confident interval of the t.test 
with dose lower than 2 does not include 0, while 95% confident interval of the 2mg test is 
centered nearly 0. This confirms the hypothesis that orange juice has a bigger impact but only when 
dose is lower than 2mg.


